---
title: "index"
author: "Christine Dunbar"
date: "2025-06-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Zuur Protocols

We are going to go through the Zuur protocols (2010). 
First step is to load libraries.

```{r libraries}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(ggcorrplot)
library(corrplot)
```

## Read in variables
 
```{r variables, echo=TRUE}
model_variables <- readRDS("~/Desktop/Analysis/Learning/learning/RDS files/model_variables.rds")
```

## Outliers

Looking for explanatory outliers 

```{r outliers, echo=TRUE}
model_variables |> 
  mutate(log_esker_camera_distances = as.numeric(esker_camera_distances)) %>%
  dplyr::select(c("Treed_broadleaf", "Treed_conifer", "Treed_mixed", "Bryoid", "Shrub", "Water", "Herbs", "gray_wolf", "grizzly_bear", "Arctic_DEM_500m_elevation_m", "esker_camera_distances", "log_esker_camera_distances", "fire_age0", "fire_age1", "fire_age2", "fire_age3", "fire_age4", "TRI_extracted", "grizzly_per_day", "gray_wolf_per_day")) %>%
  pivot_longer(cols = c("Treed_broadleaf", "Treed_conifer", "Treed_mixed", "Bryoid", "Shrub", "Water", "Herbs", "gray_wolf", "grizzly_bear", "Arctic_DEM_500m_elevation_m", "esker_camera_distances", "log_esker_camera_distances", "fire_age0", "fire_age1", "fire_age2", "fire_age3", "fire_age4", "TRI_extracted", "grizzly_per_day", "gray_wolf_per_day")) |> 
  ggplot() +
  geom_point(aes(x = value, y = rep(1:nrow(model_variables), each = n_distinct(name)))) +
  #geom_point(aes(x = value, y = name)) +
  facet_wrap(~ name, scales = "free") +
  labs(x = "Value of the variable",
       y = "Order of the data") +
  theme_bw()


model_variables |> 
  #mutate(distance_to_esker_m = as.numeric(distance_to_esker_m)) %>%
  dplyr::select(c(Muskox)) %>%
  pivot_longer(cols = c(Muskox)) |> 
  ggplot() +
  geom_point(aes(x = value, y = rep(1:nrow(model_variables), each = 1))) +
  facet_wrap(~ name, scales = "free") +
  labs(x = "Value of the variable",
       y = "Order of the data") +
  theme_bw()
```
## Testing homogeneity for variance

```{r homogenity, echo=TRUE}
model_variables |> 
  ggplot() +
  geom_boxplot(aes(y = Muskox, x = cluster)) +
  theme_bw()
```

## What are the relationships between Y and X variables?

```{r relationships, echo=TRUE}
Z <- as.vector(as.matrix(model_variables[, c("Treed_broadleaf", "Treed_conifer", "Treed_mixed", "Bryoid", "Shrub", "Water", "Herbs", "gray_wolf", "grizzly_bear", "Arctic_DEM_500m_elevation_m", "log_esker_camera_distances", "esker_camera_distances","fire_age0", "fire_age1", "fire_age2", "fire_age3", "fire_age4", "TRI_extracted", "season")]))
Y10 <- rep(model_variables$Muskox, 19)
MyNames <- names(model_variables[,c("Treed_broadleaf", "Treed_conifer", "Treed_mixed", "Bryoid", "Shrub", "Water", "Herbs", "gray_wolf", "grizzly_bear", "Arctic_DEM_500m_elevation_m", "esker_camera_distances", "log_esker_camera_distances", "fire_age0", "fire_age1", "fire_age2", "fire_age3", "fire_age4", "TRI_extracted", "season")])
ID10 <- rep(MyNames, each = length(model_variables$Muskox))
tibble(response = Y10, vars = Z, varnames = ID10) %>%
  ggplot(aes(x = vars, y = response)) +
  geom_point() +
  geom_smooth(method = "loess") +
  facet_wrap(~varnames, scales = "free")
```
## correlation matrix

Compute the correlation matrix for all numeric variables in 'model_variables'

```{r correlation, echo=TRUE}
# Select only numeric columns
numeric_data <- model_variables %>% select(where(is.numeric))

# Compute correlation matrix
cor_matrix <- cor(numeric_data, use = "complete.obs")

# Basic plot
corrplot(cor_matrix, method = "color")    
