---
title: "index"
author: "Christine Dunbar"
date: "2025-06-26"
output: html_document
---
## Packages

Load in packages. 

```{r Packages, include=TRUE}

library(vcd)
library(lme4)
library(MuMIn)
library(corrplot)
library(glmmTMB)
library(performance)
library(dplyr)
library(sf)

```

## Dataset 

Loading in dataset called "model_variables. Rmd won't save this dataset because it has a geometry column, so for this rmd I will remove that column. 

```{r Dataset, include=TRUE}

model_variables <- readRDS("~/Desktop/Analysis/Learning/learning/RDS files/model_variables.rds")

model_variables_filtered <- model_variables %>%
  filter(season == "Summer") %>%
  st_drop_geometry()

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Model 1: Global summer model with shrubs

This global summer model has shrubs but trees were excluded, because of the high collinearity. All other landcover and predator variables are included in this model. 

```{r Shrub, echo=TRUE}

mod_global_sum_shrub <- glmmTMB(Muskox ~ scale(fire_age1) + scale(log_esker_camera_distances) + scale(fire_age3) + scale(fire_age0) + scale(fire_age2) + scale(fire_age4) + scale(Shrub) + scale(Groundcover) + scale(Predators) + scale(Water) + scale(TRI_extracted) + scale(Arctic_DEM_500m_elevation_m) +
                                offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) 

summary(mod_global_sum_shrub)

```

## Model 2: Global summer model with trees

This global summer model has trees (combined broadleaf, mixed, conifer) but shrubs were excluded, because of the high collinearity. All other landcover and predator variables are included in this model. 

```{r Trees, echo=TRUE}

mod_global_sum_trees <- glmmTMB(Muskox ~ scale(fire_age1) + scale(log_esker_camera_distances) + scale(fire_age3) + scale(fire_age0) + scale(fire_age2) + scale(fire_age4) + scale(Trees) + scale(Groundcover) + scale(Predators) + scale(Water) + scale(TRI_extracted) + scale(Arctic_DEM_500m_elevation_m) +
                                  offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) 

summary(mod_global_sum_trees)

```

## Model 3: Global summer model trees-shrub 

Brad mentioned in an email (June 12) the possibility of modeling the difference between variables. Brad and I met yesterday and tried this. We called this new variable "tree_shrub" and subtracted shrubs from trees. 

```{r Third, echo=TRUE}

mod_global_sum_trees_2 <- glmmTMB(Muskox ~ scale(fire_age1) + scale(log_esker_camera_distances) + scale(fire_age3) + scale(fire_age0) + scale(fire_age2) + scale(fire_age4) + scale(tree_shrub) + scale(Groundcover) + scale(Predators) + scale(Water) + scale(TRI_extracted) + scale(Arctic_DEM_500m_elevation_m) +
                                  offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer" )%>% mutate(tree_shrub = Trees - Shrub)) 


summary(mod_global_sum_trees_2)
```

## Interpreting Results 

From all three of these summer models (shrub, trees, trees-shrub), they are telling the same story. Estimate value for trees is 0.26, shrubs is -0.26, and trees-shrub is 0.25. In plain language, muskox frequency of detections increase when tree cover increases, and muskox detections decrease with an increase of shrub cover. For predators: predator detections increase when there is an increase of muskox detections. When TRI increases, muskox detections decrease. Throughout all three models, shrubs/trees, predators, and TRI have a p-value under 0.05. From this, we can say that tree land cover and predators are influencing muskox occurrence the most out of all the variables in my dataset during the summer.




