---
title: "index"
author: "Christine Dunbar"
date: "2025-07-24"
output: html_document
---

## Looking at different model selection methods and trying to determine which will work best for my thesis. 

I will be looking at four different model selection methods in this document: StepAIC, the hypothesis driven approach, dredging and model averaging. I chose these methods as they have been brought up in past conversations with lab mates, advisors, and in articles that have performed similar research. I wanted to explore these different methods to help me get a better understanding of how each one works, and how they differ from one another. I also think it helps me overall understand my data better. 

##Packages

Load in packages.

```{r packages, include=TRUE}

library(vcd)
library(lme4)
library(MuMIn)
library(corrplot)
library(glmmTMB)
library(performance)
library(broom.mixed)
library(stringr)
library(flextable)    
library(MASS)
library(car)
library(tidyverse)
library(buildmer)
library(sf)

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset

Load in my dataset called model_variables.

```{r Dataset, include=TRUE}

model_variables <- readRDS("~/Desktop/Analysis/Learning/learning/RDS files/model_variables.rds")

model_variables_filtered <- model_variables %>%
  filter(season == "Summer") %>%
  st_drop_geometry()
```

## StepAIC

Lets look at using StepAIC on my global summer models. 

Pros to using StepAIC: 
- Minimizes model complexity 
- Enhance model performance by removing irrelevant variables
- Appropriate to make a predictive model/estimating distribution 


Cons to using StepAIC:
- "By passing the hard thinking"
- No theory underlying the approach
- Sensitive to the order of variable entry and removal 
- Can create biased estimates, standard errors, inflated p-value, and confidence intervals
- This method does not work well with the glmmTMB package, which is what I am using. I tried to use the glm.nb package for my models but I was getting convergence errors, and when I switched to the glmmTMB package, all my models ran. 

```{r StepAIC, echo=TRUE}

#scaling the variables. 

model_data <- model_variables %>% filter(season == "Summer" )
z_model_data <- MuMIn::stdize(model_data) # standarized covariates

#adding the scaled variables to dataset
model_data <- model_data %>%
  left_join(z_model_data)

#original model with all variables. fire_age2 was removed due to high collinearity with fire_age4, and trees removed due to high collinearity with shrub
mod_global_shrub <- buildglmmTMB(Muskox ~ z.log_esker_camera_distances + z.fire_age3 + z.fire_age0 + scale(fire_age1) + scale(fire_age4) + scale(Shrub) + scale(Groundcover) + scale(Predators) + scale(Water) + scale(TRI_extracted) + scale(Arctic_DEM_500m_elevation_m) +
                                 (1|cluster) + offset(log(N_days_effort)), family="nbinom2", data = model_data, 
                                 buildmerControl = buildmerControl(crit = "AIC", direction = "backward", calc.anova = TRUE, include = ~ (1|cluster) + offset(log(N_days_effort)))) 

#check_collinearity(mod_global_sum_trees_2)
mod_global_shrub@p$tab
summary(mod_global_shrub) 

```

## Hypothesis Driven Approach

Lets look at using the hypothesis driven approach on my global summer models.

Pros:
- Already put thought into what variables you should have, and what combinations there should be 
- Good for making inferences as to what matters to a species; driven by knowledge of their biology

Cons:
- Could be missing a combination of variables that is important


```{r Hypothesis, echo=TRUE}

mod_null_all_1 <- glmmTMB(Muskox ~ 1+ offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables  %>% filter(season == "Summer"))

#summer predation 
mod_pred_sum_1 <- glmmTMB(Muskox ~ scale(Predators) + offset(log(N_days_effort)) + (1|cluster),
                          family="nbinom2", data = model_variables %>% filter(season == "Summer")) #both grizz and wolf

#summer food
mod_food_sum_3 <- glmmTMB(Muskox ~ scale(Shrub) + scale(Groundcover) + scale(fire_age1) + scale(fire_age3) + scale(fire_age0) + scale(fire_age4) +
                            offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) 

mod_food_sum_3.1 <- glmmTMB(Muskox ~ scale(Shrub) + 
                              offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just shrub variable (estimate: -0.25)

mod_food_sum_3.2 <- glmmTMB(Muskox ~ scale(Groundcover) +
                            offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just herbs variable (estimate: 0.078)

mod_food_sum_3.3 <- glmmTMB(Muskox ~ scale(fire_age1) +
                              offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just fire_age1 variable (estimate: 0.2134)

mod_food_sum_3.4 <- glmmTMB(Muskox ~ scale(fire_age3) +
                              offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just fire_age3 variable (estimate: 0.008601)

mod_food_sum_3.5 <- glmmTMB(Muskox ~ scale(fire_age0) +
                              offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just fire_age0 variable (estimate: -0.04603)
mod_food_sum_3.6 <- glmmTMB(Muskox ~ scale(Shrub) + scale(Groundcover) +
                               offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running just vegetation variables for food hypothesis to compare to just fire variables 

mod_food_sum_3.7 <- glmmTMB(Muskox ~ scale(fire_age1) + scale(fire_age4) + scale(fire_age3) + scale(fire_age0) +
                              offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running just fire variables for food hypothesis


#summer thermoregulation
mod_therm_sum_4 <- glmmTMB(Muskox ~ scale(Water) + scale(log_esker_camera_distances) + scale(TRI_extracted) + scale(fire_age1) + scale(fire_age4) + scale(fire_age3) + scale(fire_age0) + scale(Arctic_DEM_500m_elevation_m) +
                             offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #all variables I think support thermoregulation hypothesis

mod_therm_sum_4.1 <- glmmTMB(Muskox ~ scale(`Water`) +
                               offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just water variable (estimate: 0.08528)

mod_therm_sum_4.2 <- glmmTMB(Muskox ~ scale(`log_esker_camera_distances`) +
                               offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just log_esker_camera_distances variable (estimate: 0.01676)

mod_therm_sum_4.3 <- glmmTMB(Muskox ~ scale(TRI_extracted)+
                               offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just water variable (estimate: 0.08528)

mod_therm_sum_4.4 <- glmmTMB(Muskox ~ scale(Arctic_DEM_500m_elevation_m) +
                             offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #all variables I think support thermoregulation hypothesis

mod_therm_sum_4.5 <- glmmTMB(Muskox ~ scale(Water) + scale(log_esker_camera_distances) + scale(TRI_extracted) + scale(Arctic_DEM_500m_elevation_m) + 
                             offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #all variables I think support thermoregulation hypothesis


mod_global <- glmmTMB(Muskox ~ scale(Water) + scale(log_esker_camera_distances) + scale(TRI_extracted) + scale(fire_age1) + scale(fire_age4) + scale(fire_age3) + scale(fire_age0) + scale(Arctic_DEM_500m_elevation_m) + scale(Shrub) + scale(Groundcover) + scale(Predators) +
                             offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer"))

fmListAll <- model.sel(mod_null_all_1=mod_null_all_1, mod_pred_sum_1=mod_pred_sum_1, mod_food_sum_3=mod_food_sum_3, mod_food_sum_3.1=mod_food_sum_3.1, mod_food_sum_3.2=mod_food_sum_3.2, mod_food_sum_3.3=mod_food_sum_3.3, mod_food_sum_3.4=mod_food_sum_3.4, mod_food_sum_3.5=mod_food_sum_3.5, mod_food_sum_3.6=mod_food_sum_3.6, mod_food_sum_3.7=mod_food_sum_3.7, mod_therm_sum_4=mod_therm_sum_4, mod_therm_sum_4.1=mod_therm_sum_4.1,
                     mod_therm_sum_4.2=mod_therm_sum_4.2, mod_therm_sum_4.3=mod_therm_sum_4.3, mod_therm_sum_4.4=mod_therm_sum_4.4,mod_therm_sum_4.5=mod_therm_sum_4.5,mod_global=mod_global)

fmListAll  

```

```{r ModelSummaries, echo=TRUE}

#mod_pred_sum_1 is the best fitting model for the first hypothesis driven approach
summary(mod_pred_sum_1)

```

```{r ModelSummaries2, echo=TRUE}

#global model is also competitive with top model for the first hypothesis driven approach
summary(mod_global)

```

## Second Approach to Hypothesis Driven Approach

Trying a different approach to the hypothesis driven approach, different hypotheses: predation, groundcover, fire and topography models instead of my original hypotheses: predation, food and thermoregulation. I'm looking at this second approach because my original models shared some of the same variables, like fire age. Both my food and thermoregulation hypotheses had fire ages 0,1,3, and 4. So for this second approach, I don't want any of the same variables to overlap with other models. I think this will help me better understand what is actually causing muskox occurrence in TDN. 

```{r SecondApproach, echo=TRUE}

mod2_null_sum_1 <- glmmTMB(Muskox ~ 1+ offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables  %>% filter(season == "Summer"))

#summer predation 
mod2_pred_sum_2 <- glmmTMB(Muskox ~ scale(Predators) + offset(log(N_days_effort)) + (1|cluster),
                          family="nbinom2", data = model_variables %>% filter(season == "Summer")) #both grizz and wolf

#summer groundcover
mod2_ground_sum_3 <- glmmTMB(Muskox ~ scale(Shrub) + scale(Groundcover) + scale(Water) +
                            offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer"))

mod2_ground_sum_3.1 <- glmmTMB(Muskox ~ scale(Shrub) + 
                              offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just shrub variable (estimate: -0.25)

mod2_ground_sum_3.2 <- glmmTMB(Muskox ~ scale(Groundcover) +
                            offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just herbs variable (estimate: 0.078)

mod2_ground_sum_3.3 <- glmmTMB(Muskox ~ scale(Water) +
                            offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just herbs variable (estimate: 0.078)

#summer fire
mod2_fire_sum_4 <- glmmTMB(Muskox ~ scale(fire_age1) + scale(fire_age4) + scale(fire_age3) + scale(fire_age0) +
                              offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running just fire variables for food hypothesis

mod2_fire_sum_4.1 <- glmmTMB(Muskox ~ scale(fire_age1) +
                              offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just fire_age1 variable (estimate: 0.2134)

mod2_fire_sum_4.2 <- glmmTMB(Muskox ~ scale(fire_age3) +
                              offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just fire_age3 variable (estimate: 0.008601)

mod2_fire_sum_4.3 <- glmmTMB(Muskox ~ scale(fire_age0) +
                              offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just fire_age0 variable (estimate: -0.04603)

mod2_fire_sum_4.4 <- glmmTMB(Muskox ~ scale(fire_age4) +
                              offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just fire_age0 variable (estimate: -0.04603)

#summer topo
mod2_topo_sum_5 <- glmmTMB(Muskox ~ scale(log_esker_camera_distances) + scale(TRI_extracted) + scale(Arctic_DEM_500m_elevation_m) +
                             offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #all variables I think support thermoregulation hypothesis

mod2_topo_sum_5.1 <- glmmTMB(Muskox ~ scale(log_esker_camera_distances) +
                               offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just water variable (estimate: 0.08528)

mod2_topo_sum_5.2 <- glmmTMB(Muskox ~ scale(TRI_extracted) +
                               offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just log_esker_camera_distances variable (estimate: 0.01676)

mod2_topo_sum_5.3 <- glmmTMB(Muskox ~ scale(Arctic_DEM_500m_elevation_m) +
                               offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) #running model with just water variable (estimate: 0.08528)


#global model
mod2_global <- glmmTMB(Muskox ~ scale(log_esker_camera_distances) + scale(TRI_extracted) + scale(fire_age1) + scale(fire_age4) + scale(fire_age3) + scale(fire_age0) + scale(Arctic_DEM_500m_elevation_m) + scale(Shrub) + scale(Groundcover) + scale(Predators) + scale(Water) +
                             offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer"))

fmListAll2 <- model.sel(mod2_null_sum_1=mod2_null_sum_1,mod2_pred_sum_2=mod2_pred_sum_2,mod2_ground_sum_3=mod2_ground_sum_3, mod2_ground_sum_3.1=mod2_ground_sum_3.1, mod2_ground_sum_3.2=mod2_ground_sum_3.2, mod2_ground_sum_3.3=mod2_ground_sum_3.3, mod2_fire_sum_4=mod2_fire_sum_4, mod2_fire_sum_4.1=mod2_fire_sum_4.1, mod2_fire_sum_4.2=mod2_fire_sum_4.2, mod2_fire_sum_4.3=mod2_fire_sum_4.3, mod2_fire_sum_4.4=mod2_fire_sum_4.4, mod2_topo_sum_5=mod2_topo_sum_5,mod2_topo_sum_5.1=mod2_topo_sum_5.1, mod2_topo_sum_5.2=mod2_topo_sum_5.2, mod2_topo_sum_5.3=mod2_topo_sum_5.3, mod2_global=mod2_global)

fmListAll2  

```
```{r Model2Summaries, echo=TRUE}

#best fitting model for second hypothesis driven approach
summary(mod2_global)

```


```{r Model2Summaries2, echo=TRUE}

#pred model is also competitive with top model for second hypothesis driven approach
summary(mod2_pred_sum_2)

```
## Plotting coefficients estimates

Plotting the coefficient estimates to visually see what variables are significant. In this example, I am plotting the coefficient estimates for the global model (mod2_global) from the second approach for the hypothesis driven approach.

```{r plotcoeficient, echo=TRUE}
#Get summary object
sum <- summary(mod2_global)

#Extract coefficients for the mean model
coef_table <- coef(sum)$cond

#Turn into a data frame
coefficients_df <- as.data.frame(coef_table)
coefficients_df$Variable <- rownames(coef_table)
rownames(coefficients_df) <- NULL

#renaming column
coefficients_df <- coefficients_df %>%
rename(Std.Error = `Std. Error`)

#Add confidence intervals
coefficients_df <- coefficients_df %>%
mutate(
Lower = Estimate - 1.96 * Std.Error,
Upper = Estimate + 1.96 * Std.Error)

#Rename categories
comp3 <- coefficients_df %>%
mutate(Variable = as.character(Variable)) %>%
mutate(Variable = dplyr::recode(Variable,
"scale(log_esker_camera_distances)" = "Distance to Esker",
"scale(TRI_extracted)" = "Terrain Ruggedness",
"scale(fire_age0)" = "0-10 Years Post Fire",
"scale(fire_age1)" = "11-20 Years Post Fire",
"scale(fire_age3)" = "21-30 Years Post Fire",
"scale(fire_age4)" = "30 Plus Years Post Fire",
"scale(Arctic_DEM_500m_elevation_m)" = "Elevation",
"scale(Shrub)" = "Shrub",
"scale(Groundcover)" = "Groundcover",
"scale(Predators)" = "Predators",
"(Intercept)"="Intercept"))

#Specify the desired order of categories
desired_order5 <- c("Distance to Esker",
"Elevation",
"Groundcover",
"Predators",
"Shrub",
"Terrain Ruggedness",
"0-10 Years Post Fire",
"11-20 Years Post Fire",
"21-30 Years Post Fire",
"30 Plus Years Post Fire",
"Intercept")

#Reorder the factor levels in the data frame
comp3$Variable <- factor(comp3$Variable, levels = desired_order5)

# Reorder factor to put Intercept last (bottom of plot)
comp3$Variable <- factor(comp3$Variable, levels = c(
  setdiff(unique(comp3$Variable), "Intercept"), "Intercept"
))

# Plot coef_estimates
coef_estimates <- ggplot(comp3,aes(x=Variable,y=Estimate)) +
geom_hline(yintercept = 0, col = "darkgrey") + # Horizontal line at y = 0
geom_point() +
geom_errorbar(aes(ymin=Lower,ymax=Upper)) +
coord_flip() +
labs(x= "Variable", y= "Coefficent estimate") +
labs(title = "Coefficent Estimates") +
theme(
axis.title.y = element_text(margin = margin(t = 0, r = 30, b = 0, l = 0)),
panel.background = element_rect(fill = 'white', colour = 'darkgrey'),
panel.grid.major = element_line(colour = 'white'),
text = element_text(size = 6), # Increase overall font size
axis.title = element_text(size = 6), # Axis titles
axis.text = element_text(size = 6)) # Axis text

#Save the plot (pdf)
ggsave(
filename = "./Plots/coef_estimates.pdf",
plot = coef_estimates,
device = "pdf", height = 10, width = 17,
units = "cm")

#Save the plot (jpeg)
ggsave(
filename = "./Plots/coef_estimates.jpg",
plot = coef_estimates,
device = "jpg", height = 10, width = 17,
units = "cm")


```

## Global Summer Models 


```{r GlobalModel, echo=TRUE}

mod_global <- glmmTMB(Muskox ~ scale(log_esker_camera_distances) + scale(fire_age3) + scale(fire_age0) + scale(fire_age1) + scale(fire_age4) + scale(Shrub) + scale(Groundcover) + scale(Predators) + scale(Water) + scale(TRI_extracted) + scale(Arctic_DEM_500m_elevation_m) +
                                offset(log(N_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) 

```


## Dredging

Pros:
- Lets you see all combinations of the variables
- Lets you see if a combination you haven't thought of is better than the combination you came up with based on hypotheses
- Appropriate method to make a predictive model/estimating distribution of a species

Cons: 
- "By passing the hard thinking"
- This method might find the strongest variables, but doesn’t always mean causation. Need to understand biology behind it!
- When dredging, you increase the chance of finding statistically significant results that are actually due to random chance, rather than a true relationship in the data.

I tried to dredge my models with all the variables in my data set and left it to run for 3 days. After 3 days it was still running, so I stopped it. It usually shouldn't take that long to dredge. I removed half of the variables in the data set and ran the dredging package again and it worked. But now, half my variables are gone that are important to include. I also received mixed opinions on whether I should use dredging in my models or not, so I took that into consideration with what model selection method I should use. 

The code I was using is below but I hashed it out because it was taking a long time to run still. I only did this for the summer months as there aren't many detections of muskox in the winter. I will not be using dredging as I think there are better options to best explain muskox occurrence in TDN, i.e. the hypothesis driven approach.

```{r Dredging, echo=TRUE}

#summer dredge
# data_summer <- model_variables %>% filter(season == "Summer")
# model_global_sum_5 <- glmmTMB(Muskox ~ scale(fire_age1) + scale(Shrub) + scale(Herbs) + scale(`Treed_broadleaf`) + scale(`Treed_conifer`) + scale(gray_wolf) + scale(grizzly_bear) + scale(TRI_extracted) +
#                                 offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = data_summer, na.action = "na.fail")
# 
# model_annual <- glmmTMB(Muskox ~ scale(`Treed_mixed`) + scale(log_esker_camera_distances) + scale(fire_age1) + scale(fire_age4) + scale(fire_age3) + scale(fire_age0) + scale(Shrub) + scale(Bryoid) + scale(Herbs) + scale(`Treed_broadleaf`) + scale(`Treed_conifer`) + scale(gray_wolf) + scale(grizzly_bear) + scale(Water) + scale(TRI_extracted) +
#                           offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = data_summer, na.action = "na.fail")
# 
# annual_dredge <- dredge(model_annual, fixed = ~offset(log(n_days_effort)) + (1|cluster))
# 
# summer_dredge <- dredge(model_global_sum_5, fixed = ~cond(offset(log(n_days_effort))) + (1|cluster))

```

## Model Averaging

Lets look at using model averaging on my global summer models.


Pros:
- Runs model between all competing models that are within 2 delta of each other 

Cons:
- Averaging together doesn’t really reflect any of the models you have
- Can mask underlying issues or make it harder to understand the relationships between variables, as it averages out potentially important differences between models
- Can still lead to over fitting, especially if a large number of models are included, some of which may not be well supported by the data
- I could be wrong, but I believe in a meeting Frances said no to model averaging. I still wanted to explore it and see how it worked. 


```{r Model Averaging, echo=TRUE}
#model averaging top models from first hypothesis driven approach
summer_top_models <- subset(fmListAll, delta <= 2)
summer_modelav <-model.avg(summer_top_models)
summary(summer_modelav)

```

```{r Model Averaging2, echo=TRUE}
#model averaging top models from second hypothesis driven approach
summer_top_models2 <- subset(fmListAll2, delta <= 2)
summer_modelav2 <-model.avg(summer_top_models2)
summary(summer_modelav2)
```
```{r Corrplot, echo=TRUE}
#looking at correlations between variables

## selecting variables for correlation matrix
subset2 <- model_variables %>%
  dplyr::select(32, 33, 34, 2, 3, 4, 5, 6, 8, 25, 28, 29, 11) %>%
  dplyr::mutate(Predators = as.numeric(Predators))

# Compute correlation matrix
cor_matrix2 <- cor(subset2, use = "complete.obs")

corrplot(cor_matrix2, method = "color", tl.cex = 0.6)
```

## Interpreting these model selection methods 

The approach that I would like to go with for my thesis is the second hypothesis driven approach I have in this document (lines 177 to 254). This is because I am guiding my models based on hypotheses that I have spent ampile time researching about that reflect the biology and life style of muskoxen. The best fitting model from this approach is mod2_global (global model, AIC = 4302.4) and the second is mod2_pred_sum_2 (grizzly bears and gray wolves, AIC = 4304.1). These were the only two models that were within 2 delta. Within the global model, the predator and fire_age1 variables best described muskox occurrence in TDN. This aligns with my hypotheses as I predicted muskox detections would increase with the increase of burned areas that were 11-20 years old (fire_age1). I also hypothesized that as muskox detections would decrease as predator detections increase, and these models support that hypothesis. Another variable that came out as significant within mod2_global was terrain ruggedness index (TRI). The estimate for TRI was -0.258, implying that muskox are not selecting areas with higher TRI. This result also supports my hypothesis for TRI in the summer, as I thought muskox would be selecting areas that have a lower TRI as it could be easier for them to move around and/or escape predators. The last variable that came out as significant in mod2_global was shrubs. The estimate for shrub was -0.241, implying that muskox are selecting against areas with more shrub cover. This result was unexpected as I thought there would be higher detections of muskox within the shrub landcover as I thought they would use that area for possible foraging. I had to remove the tree variable from my models as it was highly correlated with shrubs (see correlation matrix on line 439). 





