---
title: "index"
author: "Christine Dunbar"
date: "2025-06-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Modelling


```{r libraries}

library(vcd)
library(lme4)
library(MuMIn)
library(corrplot)
library(glmmTMB)
library(performance)
library(dplyr)
```

## Read in variables

```{r variables, echo=TRUE}
model_variables <- readRDS("~/Desktop/Analysis/Learning/learning/RDS files/model_variables.rds")
```

## Making Annual Models

I made annual models for my three hypotheses: predation, food, and thermoregulation. There is a lot of models because I wanted to see the values for each variables on their own. 

```{r annual}
mod_null_all_1 <- glmmTMB(Muskox ~ 1+ offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables)


mod_pred_all_2 <- glmmTMB(Muskox ~ scale(grizzly_bear) + scale(gray_wolf) + offset(log(n_days_effort)) + (1|cluster),
                          family="nbinom2", data = model_variables) #both grizz and wolf

mod_pred_all_2.1 <-  glmmTMB(Muskox ~ scale(grizzly_bear) + offset(log(n_days_effort)) + (1|cluster),
                             family="nbinom2", data = model_variables) #grizzly bear only

mod_pred_all_2.2 <- glmmTMB(Muskox ~ scale(gray_wolf) + offset(log(n_days_effort)) + (1|cluster),
                            family="nbinom2", data = model_variables) #gray wolf only

#annual food
mod_food_all_3 <- glmmTMB(Muskox ~ scale(Shrub) + scale(`Treed_broadleaf`) + scale(Bryoid) + scale(Herbs) + scale(fire_age1) + scale(fire_age2) + scale(fire_age3) + scale(fire_age0) +
                            offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) 

mod_food_all_3.1 <- glmmTMB(Muskox ~ scale(Shrub) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #running model with just shrub variable (estimate: -0.25)

mod_food_all_3.2 <- glmmTMB(Muskox ~ scale(Herbs) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #running model with just herbs variable (estimate: 0.078)

mod_food_all_3.3 <- glmmTMB(Muskox ~ scale(Treed_broadleaf) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #running model with just Treed_broadleaf variable (estimate: 0.107)

mod_food_all_3.4 <- glmmTMB(Muskox ~ scale(Bryoid) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #running model with just bryoid variable (estimate: -0.0123)

mod_food_all_3.5 <- glmmTMB(Muskox ~ scale(fire_age1) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #running model with just fire_age1 variable (estimate: 0.2134)

mod_food_all_3.6 <- glmmTMB(Muskox ~ scale(fire_age2) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #running model with just fire_age2 variable (estimate: -0.1442)

mod_food_all_3.7 <- glmmTMB(Muskox ~ scale(fire_age3) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #running model with just fire_age3 variable (estimate: 0.008601)

mod_food_all_3.8 <- glmmTMB(Muskox ~ scale(fire_age0) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #running model with just fire_age0 variable (estimate: -0.04603)

mod_food_all_3.9 <- glmmTMB(Muskox ~ scale(fire_age1) + scale(fire_age2) + scale(fire_age3) + scale(fire_age0) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #running just fire variables for food hypothesis

mod_food_all_3.10 <- glmmTMB(Muskox ~ scale(Shrub) + scale(`Treed_broadleaf`) + scale(Bryoid) + scale(Herbs) +
                               offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #running just vegetation variables for food hypothesis to compare to just fire variables 

#annual thermoregulation
mod_therm_all_4 <- glmmTMB(Muskox ~ scale(`Treed_mixed`)+ scale(`Treed_broadleaf`)+ scale(`Treed_conifer`)+ scale(Water) + scale(log_esker_camera_distances) + scale(fire_age1) + scale(fire_age2) + scale(fire_age3) + scale(fire_age0) + scale(TRI_extracted) +
                             offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #all variables I think support thermoregulation hypothesis

mod_therm_all_4.1 <- glmmTMB(Muskox ~ scale(`Treed_mixed`) +
                               offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #running model with just treed_mixed variable (estimate: -0.1126)

mod_therm_all_4.2 <- glmmTMB(Muskox ~ scale(`Treed_conifer`) +
                               offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #running model with just treed_conifer variable (estimate: 0.1482)

mod_therm_all_4.3 <- glmmTMB(Muskox ~ scale(`Water`) +
                               offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #running model with just water variable (estimate: 0.08528)

mod_therm_all_4.4 <- glmmTMB(Muskox ~ scale(`log_esker_camera_distances`) +
                               offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #running model with just log_esker_camera_distances variable (estimate: 0.01676)

mod_therm_all_4.5 <- glmmTMB(Muskox ~ scale(`Treed_mixed`) + scale(`log_esker_camera_distances`) + scale(`Treed_broadleaf`)+ scale(`Treed_conifer`)+ scale(Water) + scale(TRI_extracted) +
                               offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #just landcover variables, no fire

mod_global_all_5 <- glmmTMB(Muskox ~ scale(`Treed_mixed`) + scale(log_esker_camera_distances) + scale(fire_age1) + scale(fire_age2) + scale(fire_age3) + scale(fire_age0) + scale(Bryoid) + scale(Herbs) + scale(`Treed_broadleaf`) + scale(`Treed_conifer`) + scale(gray_wolf) + scale(grizzly_bear) + scale(Water) + scale(TRI_extracted) +  
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables) #this model will run with both cluster/location, and just with cluster/ just with location.
```


```{r summer}
#dropping geometry column
model_variables_nogeom <- sf::st_drop_geometry(model_variables)
summer_data <- model_variables_nogeom %>% filter(season == "Summer")



mod_null_sum_1 <- glmmTMB(Muskox ~ 1+ offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer"))

#summer predation 
mod_pred_sum_2 <- glmmTMB(Muskox ~ scale(grizzly_bear) + scale(gray_wolf) + offset(log(n_days_effort)) + (1|cluster),
                          family="nbinom2", data = summer_data %>% filter(season == "Summer")) #both grizz and wolf

mod_pred_sum_2.1 <-  glmmTMB(Muskox ~ scale(grizzly_bear) + offset(log(n_days_effort)) + (1|cluster),
                             family="nbinom2", data = summer_data %>% filter(season == "Summer")) #grizzly bear only

mod_pred_sum_2.2 <- glmmTMB(Muskox ~ scale(gray_wolf) + offset(log(n_days_effort)) + (1|cluster),
                         family="nbinom2", data = summer_data %>% filter(season == "Summer")) #gray wolf only

#summer food
mod_food_sum_3 <- glmmTMB(Muskox ~ scale(Shrub) + scale(`Treed_broadleaf`) + scale(Bryoid) + scale(Herbs) + scale(fire_age1) + scale(fire_age2) + scale(fire_age3) + scale(fire_age0) +
                            offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) 
df = model_variables %>% filter(season == "Summer")
mod_food_sum_3.1 <- glmmTMB(Muskox ~ scale(Shrub) + 
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data ) #running model with just shrub variable (estimate: -0.25)

mod_food_sum_3.2 <- glmmTMB(Muskox ~ scale(Herbs) +
                            offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) #running model with just herbs variable (estimate: 0.078)

mod_food_sum_3.3 <- glmmTMB(Muskox ~ scale(Treed_broadleaf) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) #running model with just Treed_broadleaf variable (estimate: 0.107)

mod_food_sum_3.4 <- glmmTMB(Muskox ~ scale(Bryoid) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) #running model with just bryoid variable (estimate: -0.0123)

mod_food_sum_3.5 <- glmmTMB(Muskox ~ scale(fire_age1) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) #running model with just fire_age1 variable (estimate: 0.2134)

mod_food_sum_3.6 <- glmmTMB(Muskox ~ scale(fire_age2) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) #running model with just fire_age2 variable (estimate: -0.1442)

mod_food_sum_3.7 <- glmmTMB(Muskox ~ scale(fire_age3) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) #running model with just fire_age3 variable (estimate: 0.008601)

mod_food_sum_3.8 <- glmmTMB(Muskox ~ scale(fire_age0) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) #running model with just fire_age0 variable (estimate: -0.04603)

mod_food_sum_3.9 <- glmmTMB(Muskox ~ scale(fire_age1) + scale(fire_age2) + scale(fire_age3) + scale(fire_age0) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) #running just fire variables for food hypothesis

mod_food_sum_3.10 <- glmmTMB(Muskox ~ scale(Shrub) + scale(`Treed_broadleaf`) + scale(Bryoid) + scale(Herbs) +
                            offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) #running just vegetation variables for food hypothesis to compare to just fire variables 

#summer thermoregulation
mod_therm_sum_4 <- glmmTMB(Muskox ~ scale(`Treed_mixed`)+ scale(`Treed_broadleaf`)+ scale(`Treed_conifer`)+ scale(Water) + scale(log_esker_camera_distances) + scale(fire_age1) + scale(fire_age2) + scale(fire_age3) + scale(fire_age0) + scale(TRI_extracted) +
                             offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) #all variables I think support thermoregulation hypothesis

mod_therm_sum_4.1 <- glmmTMB(Muskox ~ scale(`Treed_mixed`) +
                             offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) #running model with just treed_mixed variable (estimate: -0.1126)

mod_therm_sum_4.2 <- glmmTMB(Muskox ~ scale(`Treed_conifer`) +
                               offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) #running model with just treed_conifer variable (estimate: 0.1482)

mod_therm_sum_4.3 <- glmmTMB(Muskox ~ scale(`Water`) +
                               offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) #running model with just water variable (estimate: 0.08528)

mod_therm_sum_4.4 <- glmmTMB(Muskox ~ scale(`log_esker_camera_distances`) +
                               offset(log(n_days_effort)) + (1|cluster/location), family="nbinom2", data = summer_data %>% filter(season == "Summer")) #running model with just log_esker_camera_distances variable (estimate: 0.01676)

mod_therm_sum_4.5 <- glmmTMB(Muskox ~ scale(`Treed_mixed`) + scale(`log_esker_camera_distances`) + scale(`Treed_broadleaf`)+ scale(`Treed_conifer`)+ scale(Water) + scale(TRI_extracted) +
                               offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) 



#running global summer model with shrub and not trees 
mod_global_sum_shrub <- glmmTMB(Muskox ~ scale(fire_age1) + scale(log_esker_camera_distances) + scale(fire_age3) + scale(fire_age0) + scale(fire_age2) + scale(Shrub) + scale(Groundcover) + scale(Predators) + scale(Water) + scale(TRI_extracted) + scale(Arctic_DEM_500m_elevation_m) +
                                offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) 

#running global summer model with trees and not shrubs
mod_global_sum_trees <- glmmTMB(Muskox ~ scale(fire_age1) + scale(log_esker_camera_distances) + scale(fire_age3) + scale(fire_age0) + scale(fire_age2) + scale(Trees) + scale(Groundcover) + scale(Predators) + scale(Water) + scale(TRI_extracted) + scale(Arctic_DEM_500m_elevation_m) +
                                  offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) 

mod_global_sum_shrubs_trees <- glmmTMB(Muskox ~ scale(fire_age1) + scale(log_esker_camera_distances) + scale(fire_age3) + scale(fire_age0) + scale(fire_age2) + scale(Trees) + scale(Shrub) + scale(Groundcover) + scale(Predators) + scale(Water) + scale(TRI_extracted) + scale(Arctic_DEM_500m_elevation_m) +
                                         offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = summer_data %>% filter(season == "Summer")) 

```


```{r winter}
mod_null_win_1 <- glmmTMB(Muskox ~ 1+ offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables  %>% filter(season == "Winter"))

#winter predation
mod_pred_win_2 <- glmmTMB(Muskox ~ scale(grizzly_bear) + scale(gray_wolf) + offset(log(n_days_effort)) + (1|cluster),
                          family="nbinom2", data = model_variables %>% filter(season == "Winter")) #both grizz and wolf

mod_pred_win_2.1 <-  glmmTMB(Muskox ~ scale(grizzly_bear) + offset(log(n_days_effort)) + (1|cluster),
                             family="nbinom2", data = model_variables %>% filter(season == "Winter")) #grizzly bear only

mod_pred_win_2.2 <- glmmTMB(Muskox ~ scale(gray_wolf) + offset(log(n_days_effort)) + (1|cluster),
                            family="nbinom2", data = model_variables %>% filter(season == "Winter")) #gray wolf only

#winter food
mod_food_win_3 <- glmmTMB(Muskox ~ scale(Shrub) + scale(`Treed_broadleaf`) + scale(Bryoid) + scale(Herbs) + scale(fire_age1) + scale(fire_age2) + scale(fire_age3) + scale(fire_age0) +
                            offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) 

mod_food_win_3.1 <- glmmTMB(Muskox ~ scale(Shrub) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #running model with just shrub variable (estimate: -0.25)

mod_food_win_3.2 <- glmmTMB(Muskox ~ scale(Herbs) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #running model with just herbs variable (estimate: 0.078)

mod_food_win_3.3 <- glmmTMB(Muskox ~ scale(Treed_broadleaf) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #running model with just Treed_broadleaf variable (estimate: 0.107)

mod_food_win_3.4 <- glmmTMB(Muskox ~ scale(Bryoid) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #running model with just bryoid variable (estimate: -0.0123)

mod_food_win_3.5 <- glmmTMB(Muskox ~ scale(fire_age1) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #running model with just fire_age1 variable (estimate: 0.2134)

mod_food_win_3.6 <- glmmTMB(Muskox ~ scale(fire_age2) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #running model with just fire_age2 variable (estimate: -0.1442)

mod_food_win_3.7 <- glmmTMB(Muskox ~ scale(fire_age3) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #running model with just fire_age3 variable (estimate: 0.008601)

mod_food_win_3.8 <- glmmTMB(Muskox ~ scale(fire_age0) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #running model with just fire_age0 variable (estimate: -0.04603)

mod_food_win_3.9 <- glmmTMB(Muskox ~ scale(fire_age1) + scale(fire_age2) + scale(fire_age3) + scale(fire_age0) +
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #running just fire variables for food hypothesis

mod_food_win_3.10 <- glmmTMB(Muskox ~ scale(Shrub) + scale(`Treed_broadleaf`) + scale(Bryoid) + scale(Herbs) +
                               offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #running just vegetation variables for food hypothesis to compare to just fire variables 

#winter thermoregulation
mod_therm_win_4 <- glmmTMB(Muskox ~ scale(`Treed_mixed`)+ scale(`Treed_broadleaf`)+ scale(`Treed_conifer`)+ scale(Water) + scale(log_esker_camera_distances) + scale(fire_age1) + scale(fire_age2) + scale(fire_age3) + scale(fire_age0) + scale(TRI_extracted) +
                             offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #all variables I think support thermoregulation hypothesis

mod_therm_win_4.1 <- glmmTMB(Muskox ~ scale(`Treed_mixed`) +
                               offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #running model with just treed_mixed variable (estimate: -0.1126)

mod_therm_win_4.2 <- glmmTMB(Muskox ~ scale(`Treed_conifer`) +
                               offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #running model with just treed_conifer variable (estimate: 0.1482)

mod_therm_win_4.3 <- glmmTMB(Muskox ~ scale(`Water`) +
                               offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #running model with just water variable (estimate: 0.08528)

mod_therm_win_4.4 <- glmmTMB(Muskox ~ scale(`log_esker_camera_distances`) +
                               offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #running model with just log_esker_camera_distances variable (estimate: 0.01676)

mod_therm_win_4.5 <- glmmTMB(Muskox ~ scale(`Treed_mixed`) + scale(`log_esker_camera_distances`) + scale(`Treed_broadleaf`)+ scale(`Treed_conifer`)+ scale(Water) + scale(TRI_extracted) +
                               offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #just landcover variables, no fire

mod_global_win_5 <- glmmTMB(Muskox ~ scale(`Treed_mixed`) + scale(log_esker_camera_distances) + scale(fire_age1) + scale(fire_age2) + scale(fire_age3) + scale(fire_age0) + scale(Shrub) + scale(Bryoid) + scale(Herbs) + scale(`Treed_broadleaf`) + scale(`Treed_conifer`) + scale(gray_wolf) + scale(grizzly_bear) + scale(Water) + scale(TRI_extracted) +  
                              offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Winter")) #this model will run with both cluster/location, and just with cluster/ just with location.
```

## global summer shrubs model with no trees

making a global model with shrubs, no trees. because of high collinearity

```{r shrub}
mod_global_sum_shrub <- glmmTMB(Muskox ~ scale(fire_age1) + scale(log_esker_camera_distances) + scale(fire_age3) + scale(fire_age0) + scale(fire_age2) + scale(Shrub) + scale(Groundcover) + scale(Predators) + scale(Water) + scale(TRI_extracted) + scale(Arctic_DEM_500m_elevation_m) +
                                offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) 

summary(mod_global_sum_shrub)
```

## global summer trees model with no shrubs

making a global model with trees, no shrubs. because of high collinearity

```{r trees}
mod_global_sum_trees <- glmmTMB(Muskox ~ scale(fire_age1) + scale(log_esker_camera_distances) + scale(fire_age3) + scale(fire_age0) + scale(fire_age2) + scale(Trees) + scale(Groundcover) + scale(Predators) + scale(Water) + scale(TRI_extracted) + scale(Arctic_DEM_500m_elevation_m) +
                                  offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) 

summary(mod_global_sum_trees)
``` 


## looking at both trees and shrubs. 

just curious.

```{r both}
mod_global_sum_shrubs_trees <- glmmTMB(Muskox ~ scale(fire_age1) + scale(log_esker_camera_distances) + scale(fire_age3) + scale(fire_age0) + scale(fire_age2) + scale(Trees) + scale(Shrub) + scale(Groundcover) + scale(Predators) + scale(Water) + scale(TRI_extracted) + scale(Arctic_DEM_500m_elevation_m) +
                                         offset(log(n_days_effort)) + (1|cluster), family="nbinom2", data = model_variables %>% filter(season == "Summer")) 

summary(mod_global_sum_shrubs_trees)
```

```{r extra}
#calculating variance inflation factors (VIFs)
performance::check_collinearity(mod_global_sum_shrub)
performance::check_collinearity(mod_global_sum_trees)
performance::check_collinearity(mod_global_sum_shrubs_trees)
 
#adding bryoid and herbs together to create new variable called "groundcover"
model_variables <- model_variables %>%
mutate(Groundcover = Herbs + Bryoid)

#adding grizzly and wolves together to create new variable called "predators"
model_variables <- model_variables %>%
  mutate(Predators = gray_wolf + grizzly_bear)

#adding all trees together to create new variable called "Trees"
model_variables <- model_variables %>%
  mutate(Trees = Treed_conifer + Treed_mixed + Treed_broadleaf)
```




